--- 
title: "Spatial model with R"
author: "Federica Gazzelloni"
date: "2022 September 19"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
#bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
github-repo: fgazzelloni/How-to-Spatial-Modeling-with-R
description: "This is an ice breaking activity to spatial model with R."
---

# Prerequisites


This ice-breaking activity to spatial model with R includes two case studies:

- Oregon spotted frog habitat study
- A type of cancer spread in Scotland


It is required a good manner of RStudio and a little practice in making plots with {ggplot2}. 

To set up install the following packages:

```{r setup, include=F,	message = FALSE,warning = FALSE}

knitr::opts_chunk$set(
	eval = FALSE,
	fig.align = "center",
	fig.height = 5,
	fig.width = 8,
	message = FALSE,
	warning = FALSE,
	comment = "",
	include = FALSE
)
```


If these packages are missing in your RStudio they would need to be installed.

```{r install, eval=FALSE, include=TRUE}

my_packages <- c("tidyverse", "purrr",
                "spdep","sf","OpenStreetMap",
                 "oregonfrogs","SpatialEpi")

install.packages(my_packages, repos = "http://cran.rstudio.com")
```

The GitHub repository for this workshop is here: https://github.com/Fgazzelloni/How-to-Spatial-Modeling-with-R

